Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions

### 2015-03-24 HGmodelMANUSCRIPT/OLDversions/HGmodel_draft3.tex
move old versions to own folder

\subsection{Full hydration: Experimental order parameters for the glycerol backbone and headgroup}\label{experiments}
{\bf The specific deuteration of $\alpha$-, $\beta$- and g$_3$- segments of DPPC has been successful, 
allowing the absolute value order parameter measurements for these segments by $^2$H--NMR~\cite{gally75,brown77,brown78,akutsu81}.
In addition, the absolute values of order parameters for all glycerol backbone and choline headgroup segments in egg yolk lecithin~\cite{hong95a},
DMPC~\cite{hong95b,gross97,dvinskikh05a}, DOPC~\cite{warschawski05} and POPC~\cite{warschawski05,ferreira13}
have been measured with several different implementations of $^{13}$C NMR experiments. In addition, the signs of order parameters in some systems
are measured with $^{13}$C NMR tehcniques~\cite{hong95a,hong95b,gross97}. The experimental values of glycerol backbone 
and choline order parameters from various publications~\cite{gally75,akutsu81,gross97,dvinskikh05a,ferreira13} with the signs measured in~\cite{hong95a,hong95b,gross97} are shown in Fig.~\ref{HGorderparameters}.
}
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/comparisonSorted.pdf}
\todo{Markus Miettinen suggested that we should consider making one more figure where only experimental data would be shown and that would be discussed in Section~\ref{experiments}. \\
COMMENT: I do not think that we need such figure anymore since this figure is more clear now.} \\
\todo{I think that this figure is now very good. There is also the interactive version by Hubert Santuz now in https://plot.ly/~HubertSantuz/72/lipid-force-field-comparison/
we should figure out which is the most practical way to put that behind permalink once it finalized (Zenodo, figshare or something else?) and then put a citation in the paper.}
  \caption{\label{HGorderparameters}
  Order parameteres from simulations listed in Table~\ref{systems} and experiments for glycerol and choline groups.
  The experimental values were taken from the following publications: DMPC 303~K from \cite{gross97}, DMPC 314~K from \cite{dvinskikh05a}, DPPC 310K from \cite{gally75}, 
  DPPC 323~K from \cite{akutsu81}, and POPC 298~K \cite{ferreira13}.
  The vertical bars shown for some of the computational values are not error bars, but demonstrate that for 
  these systems we had two data sets; the ends of the bars mark the values from the two sets, and the dot marks their measurement-time-weighted average. 
  The H{\"o}gberg et al. force field in Table~\ref{systems} is abbreviated in this figure as HoNiLy, Tj{\"o}rnhammar et al. as TjoEdh, CHARMM36-UA as C36UA,
  Rabinovic et al. as RabLyu and Ulmschneider and Ulmschneider as UlmUlm.
} 
\end{figure}

>>>>

\subsection{Full hydration: Experimental order parameters for the glycerol backbone and headgroup}\label{experiments}
{\bf The specific deuteration of $\alpha$-, $\beta$- and g$_3$- segments of DPPC has been successful, 
allowing the absolute value order parameter measurements for these segments by $^2$H--NMR~\cite{gally75,brown77,brown78,akutsu81}.
In addition, the absolute values of order parameters for all glycerol backbone and choline headgroup segments in egg yolk lecithin~\cite{hong95a},
DMPC~\cite{hong95b,gross97,dvinskikh05a}, DOPC~\cite{warschawski05} and POPC~\cite{warschawski05,ferreira13}
have been measured with several different implementations of $^{13}$C NMR experiments. In addition, the signs of order parameters in some systems
are measured with $^{13}$C NMR tehcniques~\cite{hong95a,hong95b,gross97}. The experimental values of glycerol backbone 
and choline order parameters from various publications~\cite{gally75,akutsu81,gross97,dvinskikh05a,ferreira13} with the signs measured in~\cite{hong95a,hong95b,gross97} are shown in Fig.~\ref{HGorderparameters}.
}
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/comparisonSorted.pdf}
\todo{Markus Miettinen suggested that we should consider making one more figure where only experimental data would be shown and that would be discussed in Section~\ref{experiments}.
COMMENT: I do not think that we need such figure anymore since this figure is more clear now.} \\
\todo{I think that this figure is now very good. There is also the interactive version by Hubert Santuz now in https://plot.ly/~HubertSantuz/72/lipid-force-field-comparison/
we should figure out which is the most practical way to put that behind permalink once it finalized (Zenodo, figshare or something else?) and then put a citation in the paper.}
  \caption{\label{HGorderparameters}
  Order parameteres from simulations listed in Table~\ref{systems} and experiments for glycerol and choline groups.
  The experimental values were taken from the following publications:
  DMPC 303~K from \cite{gross97},
  DMPC 314~K from \cite{dvinskikh05a},
  DPPC 322~K from \cite{gally75}, 
  DPPC 323~K from \cite{akutsu81},
  POPC 296~K from \cite{bechinger91}, and
  POPC 300~K from \cite{ferreira13}.
  The vertical bars shown for some of the computational values are not error bars, but demonstrate that for 
  these systems we had at least two data sets (see Table~\ref{systems});
  the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average. 
} 
\end{figure}
